---
title: "Zero analysis"
author: "Rose Schneider"
date: "7/18/2017"
output: html_document
---

#Preliminaries
```{r setup, include=FALSE}
rm(list=ls())
library(knitr)
opts_chunk$set(cache=FALSE, message=FALSE, warning=FALSE, error=FALSE)  
```

```{r}
library(ggplot2)
library(dplyr)
library(stringr)
library(tidyr)
library(markdown)
library(magrittr)
library(langcog)
theme_set(theme_bw())

setwd("~/Documents/Projects/zero/")
```

#Data
Read in zero classification csv. Note that classifications have been done by hand, on the basis of the utterance in the context of the full corpus transcript. 
```{r}
zero_df <- read.csv('data/metadata/zero_classification.csv')
```
##Data cleaning
Excluding utterances from siblings for now - only focusing on parent/adult input. Also filtering out any utterances that could not be classified or identified. Also filtering no age data.
```{r}
zero_df %<>%
  filter(notes != "sibling", 
         !is.na(zero_type), 
         age != "[None]")
```

Create age bins
```{r}
#convert age to numeric
zero_df %<>%
  mutate(age = as.numeric(as.character(age)))

zero_df %<>%
  mutate(agebins = cut(age, c(10, 16, 22, 28, 34,
                              40, 46, 52, 58, 64, 
                              70, 76, 84, 90, 96, 
                              104, 110, 116, 122, 128), include.lowest = TRUE))
```

#Graphs
##Input vs. output over development
```{r}
ms.inout <- zero_df %>%
  group_by(agebins, input_output)%>%
  summarise(n = n())

quartz()
ggplot(ms.inout,aes(x=agebins, y=n, fill=input_output, group = input_output)) + 
  geom_bar(stat="identity", position = position_dodge()) +
  labs(x = "Age bin (months)", y = "Count") +
  scale_fill_solarized("Production/Reception")
```

##How is it used over development?
```{r}
ms.ref <- zero_df %>%
  group_by(input_output, zero_type, agebins)%>%
  summarise(n = n())

quartz()
ggplot(ms.ref,aes(x=agebins, y=n, fill = zero_type, group = zero_type)) + 
  geom_bar(stat="identity", position = position_dodge()) +
  labs(x = "Age bin (months)", y = "Count") +
  scale_fill_solarized("Production/Reception") + 
  facet_grid(zero_type~input_output, scale = "free_x")
```
That's a crazy graph, so let's simplify it a bit - nonexistence and both symbolic
```{r}
ms.ref.simp <- zero_df %>%
  group_by(input_output, zero_type, agebins)%>%
  summarise(n = n())%>%
  filter(zero_type != "count_number", 
         zero_type != "noun", 
         zero_type != "other", 
         zero_type != "symbol")

quartz()
ggplot(ms.ref.simp,aes(x=agebins, y=n, fill = zero_type, group = zero_type)) + 
  geom_bar(stat="identity", position = position_dodge()) +
  labs(x = "Age bin (months)", y = "Count") +
  scale_fill_solarized("Function") + 
  facet_grid(zero_type~input_output, scale = "free_x")
```

What is it used to refer to?
```{r}
ms.context <- zero_df %>%
  group_by(input_output,referent)%>%
  summarise(n = n())

ms.context$referent <- factor(ms.context$referent, levels=unique(with(ms.context, referent
                                  [order(ms.context$n, referent, 
                                  decreasing = TRUE)])))

quartz()
ggplot(ms.context,aes(x=referent, y=n, fill = input_output)) + 
  geom_bar(stat="identity", position = position_dodge()) +
  labs(x = "Referent", y = "Count") +
  scale_fill_solarized("Production/Reception") + 
  facet_grid(~input_output, scale = "free_x")
```

